Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
add failures

>>>>

\subsection{Failures}
\label{sec:failures}

Running workflows consisting of large numbers of tasks on distributed systems
almost always faces different types of failures. The goal of this experiment was
to asses the behaviour of the algorithms in the presence of task execution
failures by introducing a failure model into the simulator. The model is
characterized by a failure rate $f$ that defines the probability that a task
will fail. The failure time of the task is determined by randomly sampling a
time between task start and finish time. If the task fails, it is reported to
the workflow engine, which then resubmits the task for execution. Dynamic algorithms
add the task again to the priority queue (queue $P$ in Algorithm~\ref{alg:ds})
so that it can be resubmitted by the scheduler. Static algorithm resubmits the
failed task on the same VM that was selected in the plan.

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-failures-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-failures-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0 seconds to 50 \% for all three algorithms. A value of 1
    indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:failures}
\end{figure*}

Fig.~\ref{fig:failures} shows the ratios of actual values to constraints when
the failures are introduced. The high failure rates have a high impact on the
performance of the static algorithm and can degrade the solution considerably.
Comparing Fig.~\ref{fig:failures} to Figs.~\ref{fig:variances}
and~\ref{fig:delays} one may conclude that failures are worse than
provisioning delays and runtime estimate errors, since their impact is larger.
However, small failure rates (below 10\%) do not cause constraint overruns
larger than 10\%. We consider higher failure rates as rare events that suggest
some significant system malfunction or improper resource selection
process. It is thus more important that all the algorithms can handle task
failures by resubmission (as is the case of Pegasus and Condor DAGMan).
